SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Cite dataclass_transform

For the latter,
it is important to add the type annotations,
as it can provide a signature autocompletion in IDEs supporting the `dataclass_transform` (PEP 681).

>>>>

For the latter,
it is important to add the type annotations,
as it can provide a signature autocompletion in IDEs supporting the `dataclass_transform` [@debontePEP681Data2021]:
